---
title: "R/Pharma 2018 Survey"
output:
  html_document:
    theme: cerulean
    highlight: pygments
---

```{r setup, include=FALSE, warning=FALSE}

library(readxl)
library(ggplot2)
library(dplyr)
library(tidyr)
library(formattable)

knitr::opts_chunk$set(echo = FALSE)
```

```{r}

df <- read_excel('./data/attendee_survey_26Aug2018.xlsx')

```

## Content Rating

### Content Rating Day 1

```{r}
ggplot(as.data.frame(table(factor(df$qContentRatingDay1, levels = 0:10))), aes(x=Var1, y=Freq)) + geom_bar(stat='identity', fill = 'darkred') + labs(x='score', y='count') + theme_bw()
```

### Content Rating Day 2

```{r}
ggplot(as.data.frame(table(factor(df$qContentRatingDay2, levels = 0:10))), aes(x=Var1, y=Freq)) + geom_bar(stat='identity', fill = 'darkblue') + labs(x='score', y='count') + theme_bw()
```

### Keynote Rating
```{r}
ggplot(as.data.frame(table(factor(df$qKeynotesRating, levels = 0:10))), aes(x=Var1, y=Freq)) + geom_bar(stat='identity', fill = 'darkgreen') + labs(x='score', y='count') + theme_bw()
```

### Ratings for all Talks
```{r}
df.density = df[, c('qContentRatingDay1', 'qContentRatingDay2', 'qKeynotesRating')]
names(df.density) <- c('day 1', 'day 2', 'keynote')
df.density <- df.density %>%
  gather(day, rating)
ggplot(df.density, aes(rating, color = day)) + geom_density() + labs(x='score', y='count') + theme_bw()
```


## Hotels

```{r}

get_hotel <- function(hotel) {
  h_list = list(
    c(hotel = 'Sheraton', regex = 'sheraton|commander'),
    c(hotel = 'Charles', regex = 'charles'),
    c(hotel = 'Veritas', regex = 'veritas'),
    c(hotel = 'Marriott', regex = 'courtyard|marriott'),
    c(hotel = 'Hyatt', regex = 'hyatt|regency')
  )
  for (h in h_list) {
    if (grepl(h[['regex']], hotel, ignore.case = TRUE)) return (h[['hotel']])
  }
  return('other')
}

df.hotels <- df %>%
  select(response_name = qHotelName, rating = qHotelRating) %>%
  filter(!is.na(response_name)) %>%
  rowwise() %>%
  mutate(hotel = get_hotel(response_name)) %>%
  ungroup() %>%
  select(-response_name) %>%
  group_by(hotel) %>%
  count(rating) %>%
  complete(nesting(rating = 0:10)) %>%
  mutate(n = ifelse(is.na(n), 0, n))

unique_hotels <- sort(unique(df.hotels$hotel))
if ('other' %in% unique_hotels) {
  df.hotels$hotel <- factor(df.hotels$hotel, levels = c(unique_hotels[!unique_hotels == 'other'], 'other'))
} else {
  df.hotels$hotel <- factor(df.hotels$hotel, levels = unique_hotels)
}

ggplot(df.hotels, aes(x=rating, y=n)) + geom_bar(stat='identity', fill = 'darkgreen') + facet_grid(. ~ hotel)

```

## Meeting Attendance

```{r}

df_attendance <- lapply(c('qAnnualYesNo', 'qAttendNextYear', 'qAttendIfFee'), function(x) {
  df[, x] %>%
    rename('response' = !!x) %>%
    mutate(response = gsub(' ', '_', response)) %>%
    group_by(response) %>%
    count() %>%
    ungroup() %>%
    mutate(response = factor(response, levels = c('Yes', 'No', 'Not_sure'))) %>%
    mutate('percent' = as.integer(100 * n / sum(n))) %>%
    arrange(response)
})
  
```

#### Should this be an annual meeting?
`r as.htmlwidget(formattable(df_attendance[[1]], list(percent = color_bar('lightblue', fun = function(x) x/100))), width = 500)`

#### Will you attend next year?
`r as.htmlwidget(formattable(df_attendance[[2]], list(percent = color_bar('lightblue', fun = function(x) x/100))), width = 500)`

#### Would you pay a registration fee?
`r as.htmlwidget(formattable(df_attendance[[3]], list(percent = color_bar('lightblue', fun = function(x) x/100))), width = 500)`

