---
title: "R/Pharma 2018 Survey"
output:
  html_document:
    theme: cerulean
    highlight: pygments

---

```{r setup, include=FALSE, warning=FALSE}

library(readxl)
library(ggplot2)
library(dplyr)
library(tidyr)
library(formattable)
library(htmltools)
library(tm)
library(tidytext)
library(wordcloud)
library(RColorBrewer)

knitr::opts_chunk$set(echo = FALSE)
```

```{r}

df <- read_excel('./data/export_survey_13Sep2018.xlsx')

```

## Talks and Keynotes

### Content Rating Day 1

```{r}
ggplot(as.data.frame(table(factor(df$qContentRatingDay1, levels = 0:10))), aes(x=Var1, y=Freq)) + geom_bar(stat='identity', fill = 'darkred') + labs(x='score', y='count') + theme_bw()
```

### Content Rating Day 2

```{r}
ggplot(as.data.frame(table(factor(df$qContentRatingDay2, levels = 0:10))), aes(x=Var1, y=Freq)) + geom_bar(stat='identity', fill = 'darkblue') + labs(x='score', y='count') + theme_bw()
```

### Keynote Rating
```{r}
ggplot(as.data.frame(table(factor(df$qKeynotesRating, levels = 0:10))), aes(x=Var1, y=Freq)) + geom_bar(stat='identity', fill = 'darkgreen') + labs(x='score', y='count') + theme_bw()
```

### Ratings for all Talks
```{r, warning=FALSE}
df.density = df[, c('qContentRatingDay1', 'qContentRatingDay2', 'qKeynotesRating')]
names(df.density) <- c('day 1', 'day 2', 'keynote')
df.density <- df.density %>%
  gather(day, rating)
ggplot(df.density, aes(rating, color = day)) + geom_density() + labs(x='score', y='count') + theme_bw()
```

## Workshops

```{r}

df_workshops <- lapply(c('qWorkshopDay1', 'qWorkshopDay2'), function(x) {
  df_ws <- df[, x] %>%
    rename('response' = !!x) %>%
    filter(!is.na(response)) %>%
    group_by(response) %>%
    count() %>%
    ungroup() %>%
    mutate(response = factor(response)) %>%
    mutate('percent' = as.integer(100 * n / sum(n)))
  
  not_attend <- which(startsWith(as.character(df_ws$response), 'I did not attend'))
  v_order <- as.numeric(df_ws$response)
  v_order[not_attend] <- length(v_order) + 1
  df_ws$response <- reorder(df_ws$response, v_order)
  df_ws %>% arrange(response)
  
})
  
```

### Workshops Day 1
`r as.htmlwidget(formattable(df_workshops[[1]], list(percent = color_bar('lightblue', fun = function(x) x/100))), width = 500)`

### Workshops Day 2
`r as.htmlwidget(formattable(df_workshops[[2]], list(percent = color_bar('lightblue', fun = function(x) x/100))), width = 500)`


## Hotels

```{r}

get_hotel <- function(hotel) {
  h_list = list(
    c(hotel = 'Sheraton', regex = 'sheraton|commander'),
    c(hotel = 'Charles', regex = 'charles'),
    c(hotel = 'Hilton Back Bay', regex = 'hilton'),
    c(hotel = 'Veritas', regex = 'veritas'),
    c(hotel = 'Marriott', regex = 'courtyard|marriott'),
    c(hotel = 'Le Meridien', regex = 'meridien|meridian'),
    c(hotel = 'Hyatt', regex = 'hyatt|regency')
  )
  for (h in h_list) {
    if (grepl(h[['regex']], hotel, ignore.case = TRUE)) return (h[['hotel']])
  }
  return('other')
}

df.hotels <- df %>%
  select(response_name = qHotelName, rating = qHotelRating) %>%
  filter(!is.na(response_name)) %>%
  rowwise() %>%
  mutate(hotel = get_hotel(response_name)) %>%
  ungroup() %>%
  select(-response_name) %>%
  group_by(hotel) %>%
  count(rating) %>%
  complete(nesting(rating = 0:10)) %>%
  mutate(n = ifelse(is.na(n), 0, n))

unique_hotels <- sort(unique(df.hotels$hotel))
if ('other' %in% unique_hotels) {
  df.hotels$hotel <- factor(df.hotels$hotel, levels = c(unique_hotels[!unique_hotels == 'other'], 'other'))
} else {
  df.hotels$hotel <- factor(df.hotels$hotel, levels = unique_hotels)
}

ggplot(df.hotels, aes(x=rating, y=n)) + geom_bar(stat='identity', fill = 'darkgreen') + facet_grid(. ~ hotel) + scale_x_continuous(breaks = c(0,5,10))

```

```{r sentiment_analysis}

df_sentiment <- df %>%
  select(qCommentsNextYear, qComments, qWhatDidYouLikeMost, qFormatComments, qHowConvenientWasDate, qOneThingBetter
) %>%
  gather(question, response) %>%
  unnest_tokens(word, response) %>%
  inner_join(get_sentiments('bing'), by = 'word') %>%
  group_by(question) %>%
  count(sentiment) %>%
  mutate(percent = as.integer(100 * n / sum(n))) %>%
  complete(question, sentiment = c('positive', 'negative'), fill = list(n = 0, percent = 0))

```


## 2019

```{r}

df_threechoice <- lapply(c('qAnnualYesNo', 'qAttendNextYear', 'qAttendIfFee', 'qUseSlack'), function(x) {
  df[, x] %>%
    rename('response' = !!x) %>%
    mutate(response = gsub(' ', '_', response)) %>%
    group_by(response) %>%
    count() %>%
    ungroup() %>%
    mutate(response = factor(response, levels = c('Yes', 'No', 'Not_sure'))) %>%
    mutate('percent' = as.integer(100 * n / sum(n))) %>%
    arrange(response)
})
  
```

### Should this be an annual meeting?
`r as.htmlwidget(formattable(df_threechoice[[1]], list(percent = color_bar('lightblue', fun = function(x) x/100))), width = 500)`

### Will you attend next year?
`r as.htmlwidget(formattable(df_threechoice[[2]], list(percent = color_bar('lightblue', fun = function(x) x/100))), width = 500)`

### Would you pay a registration fee?
`r as.htmlwidget(formattable(df_threechoice[[3]], list(percent = color_bar('lightblue', fun = function(x) x/100))), width = 500)`

### Comments Regarding Location

```{r, warning=FALSE, results='asis'}
wordcloud(df$qCommentsNextYear, min.freq = 1, max.words = 100, random.order = F, rot.per = 0.35, colors = brewer.pal(8, "Dark2"))
```

```{r}
ggplot(df_sentiment %>% filter(question == 'qComments'), aes(x = sentiment, y = percent, fill = sentiment)) + 
  geom_bar(stat = 'identity') +
  ggtitle('Sentiment Analysis') +
  scale_y_continuous(limits = c(0, 100)) +
  coord_flip() +
  theme_bw() + 
  theme(legend.position='none')
```

```{r, results = 'asis'}
df_comments <- df[, 'qCommentsNextYear'] %>% filter(!is.na(qCommentsNextYear))
row.names(df_comments) <- NULL


HTML('<link rel="stylesheet" href="https://use.fontawesome.com/releases/v5.2.0/css/all.css" integrity="sha384-hWVjflwFxL6sNzntih27bfxkr27PmbbK/iSvJ+a4+0owXq79v+lsFkW54bOGbiDQ" crossorigin="anonymous">
      <div class="row">
        <div class="col-md-12">
          <button type="button" class="btn btn-warning btn-sm code-folding-btn" data-toggle="collapse" data-target="#table_resp1" aria-expanded="false">
            <span><i class="fas fa-plus-square" style="display: inline-block; margin-right: 10px;"></i>Conference Location Comments</span>
          </button>
        </div>
      </div>
<div id="table_resp1" class="collapse">')
format_table(df_comments, align = c('l'), col.names = NULL)
HTML('</div>')

```


## Format, Date and Venue

### Location

```{r}
ggplot(as.data.frame(table(factor(df$qVenue, levels = 0:10))), aes(x=Var1, y=Freq)) + geom_bar(stat='identity', fill = 'darkred') + labs(x='score', y='count') + theme_bw()
```

### Convenience of Date

```{r, warning=FALSE, results='asis'}
wordcloud(df$qHowConvenientWasDate, min.freq = 1, max.words = 100, random.order = F, rot.per = 0.35, colors = brewer.pal(8, "Dark2"))
```

```{r}
ggplot(df_sentiment %>% filter(question == 'qHowConvenientWasDate'), aes(x = sentiment, y = percent, fill = sentiment)) + 
  geom_bar(stat = 'identity') +
  ggtitle('Sentiment Analysis') +
  scale_y_continuous(limits = c(0, 100)) +
  coord_flip() +
  theme_bw() + 
  theme(legend.position='none')
```

```{r, results = 'asis'}
df_comments <- df[, 'qHowConvenientWasDate'] %>% filter(!is.na(qHowConvenientWasDate))
row.names(df_comments) <- NULL


HTML('<div class="row">
        <div class="col-md-12">
          <button type="button" class="btn btn-warning btn-sm code-folding-btn" data-toggle="collapse" data-target="#table_resp2" aria-expanded="false">
            <span><i class="fas fa-plus-square" style="display: inline-block; margin-right: 10px;"></i>Conference Date Comments</span>
          </button>
        </div>
      </div>
<div id="table_resp2" class="collapse">')
format_table(df_comments, align = c('l'), col.names = NULL)
HTML('</div>')

```


### General Format

```{r, warning=FALSE, results='asis'}
wordcloud(df$qFormatComments, min.freq = 1, max.words = 100, random.order = F, rot.per = 0.35, colors = brewer.pal(8, "Dark2"))
```

```{r}
ggplot(df_sentiment %>% filter(question == 'qFormatComments'), aes(x = sentiment, y = percent, fill = sentiment)) + 
  geom_bar(stat = 'identity') +
  ggtitle('Sentiment Analysis') +
  scale_y_continuous(limits = c(0, 100)) +
  coord_flip() +
  theme_bw() + 
  theme(legend.position='none')
```

```{r, results = 'asis'}
df_comments <- df[, 'qFormatComments'] %>% filter(!is.na(qFormatComments))
row.names(df_comments) <- NULL


HTML('<div class="row">
        <div class="col-md-12">
          <button type="button" class="btn btn-warning btn-sm code-folding-btn" data-toggle="collapse" data-target="#table_resp3" aria-expanded="false">
            <span><i class="fas fa-plus-square" style="display: inline-block; margin-right: 10px;"></i>General Format Comments</span>
          </button>
        </div>
      </div>
<div id="table_resp3" class="collapse">')
format_table(df_comments, align = c('l'), col.names = NULL)
HTML('</div>')

```

## Communication

### Electronic Program
```{r}
ggplot(as.data.frame(table(factor(df$qProgramRating, levels = 0:10))), aes(x=Var1, y=Freq)) + geom_bar(stat='identity', fill = 'darkblue') + labs(x='score', y='count') + theme_bw()
```

### Continue to use Slack?
`r as.htmlwidget(formattable(df_threechoice[[4]], list(percent = color_bar('lightblue', fun = function(x) x/100))), width = 500)`


## Comments

### What Did You Like Most?

```{r, warning=FALSE, results='asis'}
wordcloud(df$qWhatDidYouLikeMost, min.freq = 1, max.words = 100, random.order = F, rot.per = 0.35, colors = brewer.pal(8, "Dark2"))
```

```{r, results = 'asis'}
df_comments <- df[, 'qWhatDidYouLikeMost'] %>% filter(!is.na(qWhatDidYouLikeMost))
row.names(df_comments) <- NULL


HTML('<div class="row">
        <div class="col-md-12">
          <button type="button" class="btn btn-warning btn-sm code-folding-btn" data-toggle="collapse" data-target="#table_resp4" aria-expanded="false">
            <span><i class="fas fa-plus-square" style="display: inline-block; margin-right: 10px;"></i>What Did You Like Most?</span>
          </button>
        </div>
      </div>
<div id="table_resp4" class="collapse">')
format_table(df_comments, align = c('l'), col.names = NULL)
HTML('</div>')

```


### What Could We Do Better?

```{r, warning=FALSE, results='asis'}
wordcloud(df$qOneThingBetter, min.freq = 1, max.words = 100, random.order = F, rot.per = 0.35, colors = brewer.pal(8, "Dark2"))
```

```{r, results = 'asis'}
df_comments <- df[, 'qOneThingBetter'] %>% filter(!is.na(qOneThingBetter))
row.names(df_comments) <- NULL


HTML('<div class="row">
        <div class="col-md-12">
          <button type="button" class="btn btn-warning btn-sm code-folding-btn" data-toggle="collapse" data-target="#table_resp5" aria-expanded="false">
            <span><i class="fas fa-plus-square" style="display: inline-block; margin-right: 10px;"></i>What Could We Do Better?</span>
          </button>
        </div>
      </div>
<div id="table_resp5" class="collapse">')
format_table(df_comments, align = c('l'), col.names = NULL)
HTML('</div>')

```

### Additional Comments

```{r, warning=FALSE, results='asis'}
wordcloud(df$qComments, min.freq = 1, max.words = 100, random.order = F, rot.per = 0.35, colors = brewer.pal(8, "Dark2"))
```

```{r}
ggplot(df_sentiment %>% filter(question == 'qComments'), aes(x = sentiment, y = percent, fill = sentiment)) + 
  geom_bar(stat = 'identity') +
  ggtitle('Sentiment Analysis') +
  scale_y_continuous(limits = c(0, 100)) +
  coord_flip() +
  theme_bw() + 
  theme(legend.position='none')
```

```{r, results = 'asis'}
df_comments <- df[, 'qComments'] %>% filter(!is.na(qComments))
row.names(df_comments) <- NULL


HTML('<div class="row">
        <div class="col-md-12">
          <button type="button" class="btn btn-warning btn-sm code-folding-btn" data-toggle="collapse" data-target="#table_resp6" aria-expanded="false">
            <span><i class="fas fa-plus-square" style="display: inline-block; margin-right: 10px;"></i>Additional Comments</span>
          </button>
        </div>
      </div>
<div id="table_resp6" class="collapse">')
format_table(df_comments, align = c('l'), col.names = NULL)
HTML('</div>')
HTML('<br/><br/>')

```

## Demographics

```{r}
ggplot(df, aes(x=Country)) + 
  geom_bar(fill = 'darkgreen') + 
  theme_bw() + 
  coord_flip()
```
