---
title: "R/Pharma 2020 Survey"
output:
  html_document:
  theme: cerulean
highlight: pygments

---
  
  ```{r setup, include=FALSE, warning=FALSE}

library(readxl)
library(ggplot2)
library(dplyr)
library(tidyr)
library(formattable)
library(htmltools)
library(tm)
library(tidytext)
library(wordcloud)
library(RColorBrewer)

knitr::opts_chunk$set(echo = FALSE)
```

```{r}

df <- read_excel('./data/export-11478336.xlsx')
col_bar <- '#b71c1c'
col_percent <- '#81D4FA'

```

```{r}

df_threechoice <- lapply(c('qAttendNextYear_Virtual', 'qAttendNextYearHarvard', 'qUseSlack'), function(x) {
  df[, x] %>%
    rename('response' = !!x) %>%
    filter(!is.na(response)) %>%
    mutate(response = gsub(' ', '_', response)) %>%
    group_by(response) %>%
    count() %>%
    ungroup() %>%
    mutate(response = factor(response, levels = c('Yes', 'No', 'Not_sure'))) %>%
    mutate('percent' = as.integer(100 * n / sum(n))) %>%
    arrange(response)
})
  
```

```{r sentiment_analysis}

df_sentiment <- df %>%
  select(qLikedMost, qHopinMissing, qCommentsNextYear, qWhatDidYouLikeMost, qOneThingBetter, qComments) %>%
  gather(question, response) %>%
  unnest_tokens(word, response) %>%
  inner_join(get_sentiments('bing'), by = 'word') %>%
  group_by(question) %>%
  count(sentiment) %>%
  mutate(percent = as.integer(100 * n / sum(n))) %>%
  complete(question, sentiment = c('positive', 'negative'), fill = list(n = 0, percent = 0))

```

## Workshops and Talks

### Workshops

```{r}
ggplot(as.data.frame(table(factor(df$qWorkshopRatingNPS, levels = 0:10))), aes(x=Var1, y=Freq)) + geom_bar(stat='identity', fill = col_bar) + labs(x='score', y='count') + theme_bw()
```


### Keynotes

```{r}
ggplot(as.data.frame(table(factor(df$qKeynotesRatingNPS, levels = 0:10))), aes(x=Var1, y=Freq)) + geom_bar(stat='identity', fill = col_bar) + labs(x='score', y='count') + theme_bw()
```


### Talks

```{r}
ggplot(as.data.frame(table(factor(df$qContentRatingNPS, levels = 0:10))), aes(x=Var1, y=Freq)) + geom_bar(stat='identity', fill = col_bar) + labs(x='score', y='count') + theme_bw()
```


### Ratings for all Presentations
```{r, warning=FALSE}
df.density = df[, c('qWorkshopRatingNPS', 'qContentRatingNPS', 'qKeynotesRatingNPS')]
names(df.density) <- c('workshops', 'talks', 'keynotes')
df.density <- df.density %>%
  gather(day, rating)
ggplot(df.density, aes(rating, color = day)) + geom_density() + labs(x='score', y='count') + theme_bw()
```


## The Platform

```{r}
ggplot(as.data.frame(table(factor(df$qHopinPlatformNPS, levels = 0:10))), aes(x=Var1, y=Freq)) + geom_bar(stat='identity', fill = col_bar) + labs(x='score', y='count') + theme_bw()
```



```{r, results = 'asis'}
df_comments <- df[, 'qHopinMissing'] %>% filter(!is.na(qHopinMissing))
row.names(df_comments) <- NULL


HTML('<link rel="stylesheet" href="https://use.fontawesome.com/releases/v5.2.0/css/all.css" integrity="sha384-hWVjflwFxL6sNzntih27bfxkr27PmbbK/iSvJ+a4+0owXq79v+lsFkW54bOGbiDQ" crossorigin="anonymous">
      <div class="row">
        <div class="col-md-12">
          <button type="button" class="btn btn-warning btn-sm code-folding-btn" data-toggle="collapse" data-target="#table_resp1" aria-expanded="false">
            <span><i class="fas fa-plus-square" style="display: inline-block; margin-right: 10px;"></i>What do you think was missing from the platform</span>
          </button>
        </div>
      </div>
<div id="table_resp1" class="collapse">')
format_table(df_comments, align = c('l'), col.names = NULL)
HTML('</div>')

```

## Communication

### Rate the electronic version of the program

```{r}
ggplot(as.data.frame(table(factor(df$qProgramRatingNPS, levels = 0:10))), aes(x=Var1, y=Freq)) + geom_bar(stat='identity', fill = col_bar) + labs(x='score', y='count') + theme_bw()
```


## 2021

### Will you attend next year if we hold a virtual event?
`r as.htmlwidget(formattable(df_threechoice[[1]], list(percent = color_bar(col_percent, fun = function(x) x/100))), width = 500)`


### Will you attend next year if we hold the event at Harvard?
`r as.htmlwidget(formattable(df_threechoice[[2]], list(percent = color_bar(col_percent, fun = function(x) x/100))), width = 500)`


### Suggestions for Next Year

```{r, warning=FALSE, results='asis'}
wordcloud(df$qCommentsNextYear, min.freq = 1, max.words = 100, random.order = F, rot.per = 0.35, colors = brewer.pal(8, "Dark2"))
```

```{r, results = 'asis'}
df_comments <- df[, 'qCommentsNextYear'] %>% filter(!is.na(qCommentsNextYear))
row.names(df_comments) <- NULL


HTML('<link rel="stylesheet" href="https://use.fontawesome.com/releases/v5.2.0/css/all.css" integrity="sha384-hWVjflwFxL6sNzntih27bfxkr27PmbbK/iSvJ+a4+0owXq79v+lsFkW54bOGbiDQ" crossorigin="anonymous">
      <div class="row">
        <div class="col-md-12">
          <button type="button" class="btn btn-warning btn-sm code-folding-btn" data-toggle="collapse" data-target="#table_resp2" aria-expanded="false">
            <span><i class="fas fa-plus-square" style="display: inline-block; margin-right: 10px;"></i>Speaker Suggestions for 2021</span>
          </button>
        </div>
      </div>
<div id="table_resp2" class="collapse">')
format_table(df_comments, align = c('l'), col.names = NULL)
HTML('</div>')

```

```{r, results = 'asis'}
df_comments <- df[, 'qTopicsNextYear'] %>% filter(!is.na(qTopicsNextYear))
row.names(df_comments) <- NULL


HTML('<br/><link rel="stylesheet" href="https://use.fontawesome.com/releases/v5.2.0/css/all.css" integrity="sha384-hWVjflwFxL6sNzntih27bfxkr27PmbbK/iSvJ+a4+0owXq79v+lsFkW54bOGbiDQ" crossorigin="anonymous">
      <div class="row">
        <div class="col-md-12">
          <button type="button" class="btn btn-warning btn-sm code-folding-btn" data-toggle="collapse" data-target="#table_resp3" aria-expanded="false">
            <span><i class="fas fa-plus-square" style="display: inline-block; margin-right: 10px;"></i>Topic Suggestions for 2021</span>
          </button>
        </div>
      </div>
<div id="table_resp3" class="collapse">')
format_table(df_comments, align = c('l'), col.names = NULL)
HTML('</div>')

```

```{r, results = 'asis'}
df_comments <- df[, 'qWorkshopIdeas'] %>% filter(!is.na(qWorkshopIdeas))
row.names(df_comments) <- NULL


HTML('<br/><link rel="stylesheet" href="https://use.fontawesome.com/releases/v5.2.0/css/all.css" integrity="sha384-hWVjflwFxL6sNzntih27bfxkr27PmbbK/iSvJ+a4+0owXq79v+lsFkW54bOGbiDQ" crossorigin="anonymous">
      <div class="row">
        <div class="col-md-12">
          <button type="button" class="btn btn-warning btn-sm code-folding-btn" data-toggle="collapse" data-target="#table_resp4" aria-expanded="false">
            <span><i class="fas fa-plus-square" style="display: inline-block; margin-right: 10px;"></i>Workshop Suggestions for 2021</span>
          </button>
        </div>
      </div>
<div id="table_resp4" class="collapse">')
format_table(df_comments, align = c('l'), col.names = NULL)
HTML('</div>')

```



## Comments

### What Did You Like Most?

```{r, warning=FALSE, results='asis'}
wordcloud(df$qWhatDidYouLikeMost, min.freq = 1, max.words = 100, random.order = F, rot.per = 0.35, colors = brewer.pal(8, "Dark2"))
```

```{r, results = 'asis'}
df_comments <- df[, 'qWhatDidYouLikeMost'] %>% filter(!is.na(qWhatDidYouLikeMost))
row.names(df_comments) <- NULL


HTML('<div class="row">
        <div class="col-md-12">
          <button type="button" class="btn btn-warning btn-sm code-folding-btn" data-toggle="collapse" data-target="#table_resp5" aria-expanded="false">
            <span><i class="fas fa-plus-square" style="display: inline-block; margin-right: 10px;"></i>What Did You Like Most?</span>
          </button>
        </div>
      </div>
<div id="table_resp5" class="collapse">')
format_table(df_comments, align = c('l'), col.names = NULL)
HTML('</div>')

```


### What Could We Do Better?

```{r, warning=FALSE, results='asis'}
wordcloud(df$qOneThingBetter, min.freq = 1, max.words = 100, random.order = F, rot.per = 0.35, colors = brewer.pal(8, "Dark2"))
```

```{r, results = 'asis'}
df_comments <- df[, 'qOneThingBetter'] %>% filter(!is.na(qOneThingBetter))
row.names(df_comments) <- NULL


HTML('<div class="row">
        <div class="col-md-12">
          <button type="button" class="btn btn-warning btn-sm code-folding-btn" data-toggle="collapse" data-target="#table_resp6" aria-expanded="false">
            <span><i class="fas fa-plus-square" style="display: inline-block; margin-right: 10px;"></i>What Could We Do Better?</span>
          </button>
        </div>
      </div>
<div id="table_resp6" class="collapse">')
format_table(df_comments, align = c('l'), col.names = NULL)
HTML('</div>')

```

### Additional Comments

```{r, warning=FALSE, results='asis'}
wordcloud(df$qComments, min.freq = 1, max.words = 100, random.order = F, rot.per = 0.35, colors = brewer.pal(8, "Dark2"))
```

```{r}
ggplot(df_sentiment %>% filter(question == 'qComments'), aes(x = sentiment, y = percent, fill = sentiment)) + 
  geom_bar(stat = 'identity') +
  ggtitle('Sentiment Analysis') +
  scale_y_continuous(limits = c(0, 100)) +
  coord_flip() +
  theme_bw() + 
  theme(legend.position='none')
```

```{r, results = 'asis'}
df_comments <- df[, 'qComments'] %>% filter(!is.na(qComments))
row.names(df_comments) <- NULL


HTML('<div class="row">
        <div class="col-md-12">
          <button type="button" class="btn btn-warning btn-sm code-folding-btn" data-toggle="collapse" data-target="#table_resp7" aria-expanded="false">
            <span><i class="fas fa-plus-square" style="display: inline-block; margin-right: 10px;"></i>Additional Comments</span>
          </button>
        </div>
      </div>
<div id="table_resp7" class="collapse">')
format_table(df_comments, align = c('l'), col.names = NULL)
HTML('</div>')
HTML('<br/><br/>')

```



